\chapter{Egy slapd.conf állomány}
\begin{Verbatim}
#
# See slapd.conf(5) for details on configuration options.
# This file should NOT be world readable.
#
include         /etc/openldap/schema/core.schema
include         /etc/openldap/schema/cosine.schema
include         /etc/openldap/schema/inetorgperson.schema
include         /etc/openldap/schema/nis.schema
include         /etc/openldap/schema/misc.schema
include         /etc/openldap/schema/samba.schema

# Define global ACLs to disable default read access.

# Do not enable referrals until AFTER you have a working directory
# service AND an understanding of referrals.
#referral       ldap://root.openldap.org

pidfile         /var/run/openldap/slapd.pid
argsfile        /var/run/openldap/slapd.args

# Load dynamic backend modules:
# modulepath    /usr/lib/openldap/openldap
# moduleload    back_bdb.la
# moduleload    back_ldap.la
# moduleload    back_ldbm.la
# moduleload    back_passwd.la
# moduleload    back_shell.la

# Sample security restrictions
#       Require integrity protection (prevent hijacking)
#       Require 112-bit (3DES or better) encryption for updates
#       Require 63-bit encryption for simple bind
#security ssf=1 update_ssf=112 simple_bind=64

# Sample access control policy:
#       Root DSE: allow anyone to read it
#       Subschema (sub)entry DSE: allow anyone to read it
#       Other DSEs:
#               Allow self write access
#               Allow authenticated users read access
#               Allow anonymous users to authenticate
#       Directives needed to implement policy:
# access to dn.base="" by * read
# access to dn.base="cn=Subschema" by * read
# access to *
#       by self write
#       by users read
#       by anonymous auth
#
# if no access controls are present, the default policy
# allows anyone and everyone to read anything but restricts
# updates to rootdn.  (e.g., "access to * by * read")
#


access to attrs=userPassword
        by dn="cn=admin,dc=panthernet" write
        by anonymous auth
        by self write
        by * none

# The admin dn has full write access
access to dn.children="ou=People,dc=panthernet"
        by dn="cn=admin,dc=panthernet" write
        by * read


# rootdn can always read and write EVERYTHING!

sasl-realm panthernet
sasl-regexp uid=([^,]+),.*cn=GSSAPI,.* uid=$1,ou=People,dc=panthernet
sasl-host zeratul.panthernet

############ TLS #######
TLSCACertificateFile /etc/openldap/ssl/cacert.pem
TLSCertificateFile /etc/openldap/ssl/ldaps.panthernet.crt
TLSCertificateKeyFile /etc/openldap/ssl/ldaps.panthernet.key
TLSCipherSuite HIGH,MEDIUM


#######################################################################
# BDB database definitions
#######################################################################

database        bdb
suffix          "dc=panthernet"
rootdn          "cn=Manager,dc=panthernet"
# Cleartext passwords, especially for the rootdn, should
# be avoid.  See slappasswd(8) and slapd.conf(5) for details.
# Use of strong authentication encouraged.
rootpw         {SSHA}stb.

checkpoint      32      30 # <kbyte> <min>


# The database directory MUST exist prior to running slapd AND
# should only be accessible by the slapd and slap tools.
# Mode 700 recommended.
directory       /var/lib/openldap-data
# Indices to maintain
index   objectClass     eq

LogLevel 0
\end{Verbatim}



% Local Variables:
% fill-column: 120
% TeX-master: t
% End:
